Analysis paper

### 2021-08-21 analysis/analysis.Rmd
update plots

@@

  trend <- 
    copy(epitrend)[, location_target := paste0(str_to_sentence(target_type), 
                                               "s", " in ", location_name)]
  setnames(trend, old = c("classification"), new = c("Classification"))
  p <- df %>%
    dplyr::filter(target_type == ttype) %>%
    ggplot(aes(y = true_value, x = target_end_date)) + 
    geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = Model), 
                   size = 1.1,
                   alpha = 1,
                   position = position_dodge(width = 3.6)) + 
    geom_point(data = trend[target_type == ttype],
               aes(shape = Classification)) +
    geom_line(data = unfiltered_data[target_type == ttype & horizon == 2]) + 
    theme_minimal() + 
    theme(panel.grid.major.x = element_blank()) +
    facet_wrap(~ location_target, scales = "free", ncol = 2) + 
    theme(legend.position = "bottom") + 
    scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 5, 
                            max(forecast_dates$full_hub_period)), 
                 minor_breaks = forecast_dates$unfiltered + 5)
  return(p)
}

scores_over_time_plot <- function(scores, y = "mean_scores_ratio") {
  p <- scores %>%
    ggplot(aes(x = as.Date(target_end_date), y = get(y))) + 
    geom_line(aes(colour = model)) + 
    geom_point(aes(colour = model, shape = classification)) + 
    theme_minimal() + 
    facet_wrap( ~ location_target, ncol = 2, scales = "free_y") +
    theme(legend.position = "bottom") +
    scale_y_continuous(labels = comma) + # , 
                       # trans = log_trans()) +
    scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 5, 
                            max(forecast_dates$full_hub_period)))
  return(p)
}

@@

    # truth plot for cases 
    truth_vs_forecast_cases <- df[grepl(i, target)] %>%
      truth_and_pred_plot(ttype = "case") + 
      scale_color_manual(values = colcases) + 
      labs(y = "Cases", x = "")

    # truth plot for deaths
    truth_vs_forecast_deaths <- df[grepl(i, target)] %>%
      truth_and_pred_plot(ttype = "death")  + 
      scale_color_manual(values = coldeaths) + 
      annotate('rect', xmin = min(forecast_dates$full_hub_period) + 14,
               xmax = max(forecast_dates$death_not_scored) + 14,
               ymin = 0,
               ymax = Inf, fill = "grey10", alpha = 0.1) + 
      labs(y = "Deaths", x = "") +
      theme(legend.position = "none") + 
      guides(color = "none", shape = "none")

    # scores plot for cases
    scores_over_time_cases <- 
      scores_target_forecastdate[horizon == i & target_type == "case"] %>%
      merge(epi_tmp) %>%
      scores_over_time_plot(y = "interval_score") + 
      scale_color_manual(values = colcases) + 
      labs(y = "WIS", x = "") + 
      theme(legend.position = "none") + 
      guides(color = "none", shape = "none")

    # scores plot for deaths
    scores_over_time_deaths <- 
      scores_target_forecastdate[horizon == i & target_type == "death"] %>%
      merge(epi_tmp) %>%
      scores_over_time_plot(y = "interval_score") + 
      scale_color_manual(values = coldeaths) + 
      annotate('rect', xmin = min(forecast_dates$full_hub_period) + 14,
               xmax = max(forecast_dates$death_not_scored) + 14,
               ymin = 0,
               ymax = Inf, fill = "grey10", alpha = 0.1) + 
      labs(y = "WIS", x = "Date") + 
      theme(legend.position = "none") + 
      guides(color = "none", shape = "none")

    # putting them all together
    truth_vs_forecast_cases / scores_over_time_cases / 
      truth_vs_forecast_deaths / scores_over_time_deaths + 
      plot_layout(guides = "collect") & 
      # guides(fill = "guidetitle") &
      plot_annotation(tag_levels = 'A') &
      theme(legend.position = 'bottom')

    ggsave(here(output_dir, 
                paste0(plotname, "-", i, ".png")), width = 10, height = 12)

>>>>

  if (ttype == "case") {
    dodgewidth = 3.6
  } else {
    dodgewidth = 3.7
  }

@@

  trend <- 
    copy(epitrend)[, location_target := paste0(str_to_sentence(target_type), 
                                               "s", " in ", location_name)]
  setnames(trend, old = c("classification"), new = c("Classification"))

  limits <- min(forecast_dates$full_hub_period) + 5 + 1:21 * 7

  p <- df %>%
    dplyr::filter(target_type == ttype) %>%
    ggplot(aes(y = true_value, x = target_end_date)) + 
    geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = Model), 
                   size = 1.1,
                   alpha = 1,
                   position = position_dodge(width = dodgewidth)) + 
    geom_point(data = trend[target_type == ttype],
               aes(shape = Classification)) +
    geom_line(data = unfiltered_data[target_type == ttype & horizon == 2]) + 
    theme_minimal() + 
    theme(panel.grid.major.x = element_blank()) +
    facet_wrap(~ location_target, scales = "free", ncol = 1) + 
    theme(legend.position = "bottom") + 
    scale_x_date(limits = c(min(limits), max(limits)), 
                 minor_breaks = limits)
  return(p)
}

scores_over_time_plot <- function(scores, y = "mean_scores_ratio") {
  limits <- min(forecast_dates$full_hub_period) + 5 + 1:21 * 7

  p <- scores %>%
    ggplot(aes(x = as.Date(target_end_date), y = get(y))) + 
    geom_line(aes(colour = model)) + 
    geom_point(aes(colour = model, shape = classification)) + 
    theme_minimal() + 
    facet_wrap( ~ location_target, ncol = 1, scales = "free") +
    theme(legend.position = "bottom") +
    theme(panel.grid.major.x = element_blank()) +
    scale_y_continuous(labels = comma) + # , 
                       # trans = log_trans()) + 
    scale_x_date(limits = c(min(limits), max(limits)), 
                 minor_breaks = limits)
  return(p)
}

@@

    # truth plot for cases 
    truth_vs_forecast_cases <- df[grepl(i, target)] %>%
      truth_and_pred_plot(ttype = "case") + 
      scale_color_manual(values = colcases) + 
      labs(y = "Forecasts and observed values", x = "")  + 
      theme(legend.position = "none") +
      guides(color = "none", shape = "none") + 
      theme(plot.margin = unit(c(0.5,1.3,0.5,0.5), "cm"))

    # truth plot for deaths
    truth_vs_forecast_deaths <- df[grepl(i, target)] %>%
      truth_and_pred_plot(ttype = "death")  + 
      scale_color_manual(values = coldeaths) + 
      annotate('rect', xmin = min(forecast_dates$full_hub_period) + 14,
               xmax = max(forecast_dates$death_not_scored) + 14,
               ymin = 0,
               ymax = Inf, fill = "grey10", alpha = 0.1) + 
      labs(y = "Forecasts and observed values", x = "") +
      theme(legend.position = "none") +
      guides(color = "none", shape = "none") + 
      theme(plot.margin = unit(c(0.5,1.3,0.5,0.5), "cm"))

    # scores plot for cases
    scores_over_time_cases <- 
      scores_target_forecastdate[horizon == i & target_type == "case"] %>%
      merge(epi_tmp) %>%
      scores_over_time_plot(y = "interval_score") + 
      scale_color_manual(values = colcases) + 
      labs(y = "Weighted interval score", x = "") + 
      theme(legend.position = "none") +
      guides(color = "none", shape = "none")

    # scores plot for deaths
    scores_over_time_deaths <- 
      scores_target_forecastdate[horizon == i & target_type == "death"] %>%
      merge(epi_tmp) %>%
      scores_over_time_plot(y = "interval_score") + 
      scale_color_manual(values = coldeaths) + 
      annotate('rect', xmin = min(forecast_dates$full_hub_period) + 14,
               xmax = max(forecast_dates$death_not_scored) + 14,
               ymin = 0,
               ymax = Inf, fill = "grey10", alpha = 0.1) + 
      labs(y = "Weighted interval score", x = "")

    # putting them all together
    p <- (truth_vs_forecast_cases + scores_over_time_cases) / 
      (truth_vs_forecast_deaths + scores_over_time_deaths) + 
      plot_layout(guides = "collect") &
      plot_layout(widths = c(1.9, 1)) &
      plot_annotation(tag_levels = 'A') &
      theme(legend.position = 'bottom', 
            legend.box="vertical", legend.margin = margin())

    ggsave(here(output_dir, 
                paste0(plotname, "-", i, ".png")), width = 10, height = 11)
